
% Langmuir probes, as well as other instruments, are often situated outside of space crafts.
% The precence of the spacecraft causes disturbances to the local conditions we want to measure,
% these disturbances need to be corrected for.
% Many studies has been done on the flow of plasma around spacecraft and of the wake the
% spacecraft creates \citep{miloch_wake_2010,engwall_wake_2006}.

A spacecraft in space will always be affected by its environment, resulting in various
impacts depending on the orbit (location), types of materials as well as the environment
condition that changes over time \citep{trove.nla.gov.au/work/21680840}. The  most common phenomena on the spacecraft is the so
called charging. The level of charging depends on the energy of particles interacting with
the spacecraft. At lower levels of energy, the form of interaction of charged particles with the
spacecraft only affect the surface part called surface charging. However, for higher levels of energy
worse affects might occur, and in this case the charged particles
can penetrate deep inside the spacecrafts components resulting in so called internal charging \citep{fennell2001spacecraft}.

Charging on the spacecraft can be simulated numerically. Numerous codes have been developed
to explain the behavior of particles around the spacecraft as well as their interactions.
Nevertheless, there still remains many questions since the numerical simulations are only approximations
of real conditions. Although the numerical approach has given good solutions to various applications
such as spaceflight missions. Efforts are made to prove the reliability of a well before launch into space.
One of these efforts is simulating the environment where the satellite will be placed during its mission.
Many parameters are taken into account with respect to its effect on the spacecraft.
The results of the simulations can be a significant point in the decisions made for the spaceflight
mission. This is one of reasons why numerical methods are the primary interest for this study.

In this study, we attempt to simulate a spacecraft named Norsat-1 which will be placed in
Low Earth Orbit (LEO) environment around \(600\) km altitude and polar inclination around \(98.8^\circ\).
This spacecraft is planned to launch in \(2017\)\citep{norSat}. Our simulation was of a smaller spacecraft with dimensions
\(10,10,10\)cm.
This satellite
has been equipped with two probes. It is interesting since this satellite will pass over
the auroral region more frequently. In this region  the satellite will be exposed not only to
rapid variation of the thermal component of the ionosphere \citep{hastings1995review}, but also to high
energy particles from the solar wind, large changes in the direction of the magnetic field, etc.

Since we use the EMSES (Electro Magnetic Spacecraft Environment Simulator) code \citep{miyake_plasma_2013} in the
simulation, it is important to point out that only the effects of background plasma as
well as the photoelectrons from the sunlight are taken into account. The simulations
are done in several cases and each case has been grouped into two, i.e. plasma
flows with and without the photoemission effects on the spacecraft as well as the probes.
All results will be presented in detail in the specific section in this report.
